When are Fuzzy Extractors Possible?

### 2014-07-18 info-bounds/FuzzyExtPossibility.tex
adding work on distribution agnostic sketches

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
\]
\end{definition}
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  In the interactive setting, fuzzy min-entropy is also a sufficient condition using secure two-party computation\bnote{cite something for this}.  However, in the non-interactive setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.  We attempt to bridge this gap in this work.

\section{Well-spread distributions}
In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.  We begin by considering secure sketches.  We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Intuitively, no sketch should be necessary for such a distribution.  However, we show there is a large gap between a secure sketch that works for a particular well-spread distribution and a secure sketch that works for \emph{all} well-spread distributions.

\begin{table}
\begin{tabular}{l | l | c}
Upper bound & Depends on Distribution & Works for all Dist\\
\hline
Well-spread distribution & $0$ & $\log |B_t|$\\
Flat distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta)$ &$\log |B_t|$\\
Arbitrary distribution & $\Hoo(W) - \Hfuzz(W) + \log (1/\delta) + \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\caption{Upper bounds on minimum number of bits that a secure sketch can write down and still recovery with overwhelming probability.}
\label{tab:upper bounds}
\end{table}
\subsection{Distribution-Dependent Sketches}
Error-correction should be easy when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.  Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  We begin by defining a well-spread distribution.

@@

\subsection{Distribution-Agnostic Sketches}
Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

The above lemma only talks about how many bits the algorithms must write down.  It does not say that the entropy of the distribution must decrease~(this is the important question).

\section{Flat distributions}
In the previous section we showed bounds on producing secure sketches and fuzzy extractors for well-spread distributions.  In this section we further investigate secure sketches where the sketch depends on the input distribution.\footnote{Recall the bound when the sketch does not know the input distribution is $\log |B_t|$ bits and this is constructible for any distribution.}

\subsection{Distribution-Dependent Sketches}

\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp. secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.  In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.  
We begin by considering flat distributions where the probability of each point in $W$ is the same.

@@

Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme~(\defref{def:fuzzy min-ent}).  Fuzzy min-entropy is total weight of the maximum probability ball.  For flat distribution, this is directly correlated to the ball with the largest number of points.  That is, for a flat distribution 
\begin{align*}
\Hfuzz(W) &= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} * \Pr[W=w]\\
&= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} *2^{-\Hoo(W)}\\
&=\Hoo(W) -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} 
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}
%We start by considering distributions that have a fixed number of neighbors for each point.
%
%\begin{definition}
%We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.  We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
%\end{definition}
%
%\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
We now present an information-theoretic construction for flat distributions.  We first introduce the notion of a pairwise-independent hash:

@@

\section{Arbitary distributions}
The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.

@@

\subsection{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.

@@

\subsection{Layered Hashing}
\label{sec:layered hash}
In the previous section, we saw that sketching non-flat distributions is difficult~(while retaining entropy close to the fuzzy min-entropy).  The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.  We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.  Then the hash is applied only considering the maximum weight of the ball containing points at this level.  Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.  Naturally, revealing the probability of the original point leaks some information and there is a balance between how much about the probability is revealed to the adversary and how useful it is.

@@

\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
\]
\end{definition}
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  In the interactive setting, fuzzy min-entropy is also a sufficient condition using secure two-party computation\bnote{cite something for this}.  However, in the non-interactive setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.  We attempt to bridge this gap in this work.  The summary of our results is in Table~\ref{tab:upper bounds}.

\begin{table}
\begin{tabular}{l | l | c}
Lower bounds & Distribution-Dependent & Distribution-Agnostic\\
\hline
Well-spread distribution & $\Hfuzz(W)$ & $\log |B_t|$\\
Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\caption{Residual entropy of secure sketches for complete recovery.}
\label{tab:upper bounds}
\end{table}
\bnote{Fix right side of table}
We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

\section{Distribution-Dependent Sketches}
In the remainder of this work, we consider increasingly complex types of distributions and consider both the minimum number of bits a secure sketch/fuzzy extractor must write down and the minimum entropy loss.  We begin by considering secure sketches.  We consider the setting where the algorithms have a complete description of the distribution $W$.  In the next setting we consider the setting where the construction must work for a family of distributions~(we show there is a large gap between these two settings).

\subsection{Well-Spread Distributions}
We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction should be easy when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.  Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  We begin by defining a well-spread distribution.

@@

\subsection{Flat distributions}
In the previous section we showed that info-theoretically it is easy to produce a secure sketch and fuzzy extractor for a well-spread distribution when the algorithms are allowed to encode the input distribution $W$.  
%\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp. secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.  
In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.  
We begin by considering flat distributions where the probability of each point in $W$ is the same.

@@

Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme (\defref{def:fuzzy min-ent}).  Fuzzy min-entropy is total weight of the maximum probability ball.  For flat distribution, this is directly correlated to the ball with the largest number of points.  That is, for a flat distribution 
\begin{align*}
\Hfuzz(W) &= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} * \Pr[W=w]\\
&= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} *2^{-\Hoo(W)}\\
&=\Hoo(W) -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} 
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}
%We start by considering distributions that have a fixed number of neighbors for each point.
%
%\begin{definition}
%We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.  We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
%\end{definition}
%
%\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
We now present an information-theoretic construction for flat distributions.  We first introduce the notion of a pairwise-independent hash:

@@

\subsection{Arbitary distributions}
The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.

@@

\subsubsection{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.

@@

\subsubsection{Layered Hashing}
\label{sec:layered hash}
In the previous section, we saw that sketching non-flat distributions is difficult~(while retaining entropy close to the fuzzy min-entropy).  The problem is distinguishing between the setting where a ball has a few high probability points and a large number of low probability points.  We will deal with this problem by describing the probability of the point $w_0\in W$ seen in sketch.  Then the hash is applied only considering the maximum weight of the ball containing points at this level.  Roughly, at each layer we can think of the distribution as being flat, and the only additional information is the layer of the original reading.  Naturally, revealing the probability of the original point leaks some information and there is a balance between how much about the probability is revealed to the adversary and how useful it is.

@@

\section{Distribution-Agnostic Sketches}
Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

The above lemma only talks about how many bits the algorithms must write down.  It does not say that the entropy of the distribution must decrease~(this is the important question).  We now proceed to this question.

\subsection{Min-Max to switch quantifiers}

\subsection{Impossibility of info-theoretic sketches for distribution}
\begin{lemma}
There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
\end{lemma}

\begin{corollary}
This is also impossible for computational sketches that retain hill entropy.
\end{corollary}

\subsection{Conductors}
Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
\begin{lemma}
Not possible for information-theoretic objects.
\end{lemma}
\bibliographystyle{alpha}
\bibliography{crypto}
